---
title: "Vignette 1"
author: "Gabriele Pittarello"
date: "`r Sys.Date()`"
bibliography: '`r system.file("references.bib", package="clmplus")`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Case study part 1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r tailor made functions, include=FALSE}
t2c <- function(x){
  "
  Function to transform an upper run-off triangle into a half-square.
    
  This function takes an upper run-off triangle as input.
  
  It returns a half square.
  "
  I= dim(x)[1]
  J= dim(x)[2]
  
  mx=matrix(NA,nrow=I,ncol=J)
  for(i in 1:(I)){
    for(j in 1:(J)){
      if(i+j<=J+1){
        mx[j,(i+j-1)]=x[i,j]
      }
    }
  }
  return(mx)
}


c2t <- function(x){
  "
  Function to transform a square into an upper run-off triangle.
  
  This function takes a half square as input.
  
  It returns an upper run-off triangle. 
  "
  I= dim(x)[1]
  J= dim(x)[2]
  
  mx=matrix(NA,nrow=I,ncol=J)
  for(i in 1:(I)){
    for(j in 1:(J)){
      if(i+j<=J+1){
        mx[i,j]=x[j,(i+j-1)]
      }
    }
  }
  return(mx)
}


```



# Introduction

The `clmplus` package aims to offer a fast and user-friendly implementation of the modeling framework introduced in our paper, @pittarello25.

In this vignette:

* We replicate the chain-ladder model using an age-model for the claim development. We can replicate the chain ladder model using an age-model for the claim development. As discussed in the paper, modeling claim development allows us to replicate chain-ladder estimate for claims reserve using fewer parameters than modeling claim amounts (@england99).

* We provide an example illustrating how incorporating a cohort effect can enhance model fit.

Before proceeding, we summarise in a table the notation of the claim development models implemented in `clmplus` package. The implementation of the models for the claim development available in the `clmplus` is based on the implementation of the models for human mortality implemented in the `StMoMo` package. Users can either rely on our default models or set their own configuration for the claim development. 


|      Model      | Lexis dimension                 |Claims reserving                  |
| :-------------: |:-------------------------------:|---------------------------------:|
| a               | age                             |development (chain-ladder model)  |
| ac              | age-cohort                      |development-accident              |
| ap              | age-period                      |development-calendar              |
| apc             | age-period-cohort               |development-calendar-accident     |



# Replicate the chain-ladder with the `clmplus` package

For this tutorial, we use the `AutoBIPaid` run-off triangle available in the `ChainLadder` package (@chainladderpackage).

```{r input data cl package, include= FALSE}
library(ChainLadder)

data("AutoBI")
dataset=AutoBI$AutoBIPaid 


input_data <- incr2cum(dataset)

```

The data is pre-processed using the `AggregateDataPP` method.

```{r pp_data data, include=FALSE}
library(clmplus)


pp_data <- AggregateDataPP(cumulative.payments.triangle = input_data)

```

The desired model is fit using the `clmplus` method.

```{r amodel, message=FALSE, warning=FALSE}
a.model.fit=clmplus(AggregateDataPP =  pp_data, 
             hazard.model = "a")

```

Out of the fitted model, it is possible to extract the fitted development factors:

```{r amodeloutput1, message=FALSE}

a.model.fit$fitted_development_factors

```
It is also possible to extract the fitted effects on the claims development.

```{r amodeloutput2, message=FALSE}

a.model.fit$fitted_effects

```
Predictions can be computed with the `predict` method.

```{r amodelpredict, message=FALSE}

a.model <- predict(a.model.fit)

```

Out of the model predictions, we can extract the predicted development factors, the full and lower triangle of predicted cumulative claims.

```{r dfpredicted, message=FALSE}

a.model$development_factors_predicted

```

```{r ltpredicted, message=FALSE}

a.model$lower_triangle

```

```{r ftpredicted, message=FALSE}

a.model$full_triangle

```

We can also predict for different forecasting horizons. Below predictions for one calendar period ahead. The forecasting horizon can be specified with the `forecasting_horizon` argument in the `predict` method.

```{r predictionsoneyear, message=FALSE}

a.model.2 <- predict(a.model.fit,
                     forecasting_horizon=1)

```

We compare our estimates with those obtained with the Mack chain-ladder method (@mack93) as implemented in the `ChainLadder` package. We predict the same reserve as the literature benchmark.

```{r mack, message=FALSE, warning=FALSE}
mck.chl <- MackChainLadder(input_data)
ultimate.chl=mck.chl$FullTriangle[,dim(mck.chl$FullTriangle)[2]]
diagonal=rev(t2c(mck.chl$FullTriangle)[,dim(mck.chl$FullTriangle)[2]])
```

Estimates are gathered in a `data.frame` for comparison.

```{r clm replicated}
data.frame(ultimate.cost.mack=ultimate.chl,
           ultimate.cost.clmplus=a.model$ultimate_cost,
           reserve.mack=ultimate.chl-diagonal,
           reserve.clmplus=a.model$reserve
           )

cat('\n Total reserve:',
    sum(a.model$reserve))

```

## Claims reserving with GLMs compared to hazard models

We fit the stochastic model replicating the chain-ladder with an age-cohort GLM for the claim amounts described in @england99 using the `apc`package @apcpackage. 

```{r apc clm}
library(apc)

ds.apc = apc.data.list(cum2incr(dataset),
                       data.format = "CL")

ac.model.apc = apc.fit.model(ds.apc,
                         model.family = "od.poisson.response",
                         model.design = "AC")

```

Inspect the model coefficients derived from the output:

```{r show comparison}

ac.model.apc$coefficients.canonical[,'Estimate']

ac.fcst.apc = apc.forecast.ac(ac.model.apc)

data.frame(reserve.mack=ultimate.chl-diagonal,
           reserve.apc=c(0,ac.fcst.apc$response.forecast.coh[,'forecast']),
           reserve.clmplus=a.model$reserve
           
           )


```

Our method is able to replicate the chain-ladder results without adding the cohort component.

```{r fitted ax amodel}
a.model.fit$fitted_effects

```

Further inspection can be performed with the `clmplus` package, which provides the graphical tools to inspect the fitted effects. The fitted effects can be plotted using the `plot` function on the output of the `predict` method.

```{r plot effects ax, message=FALSE, warning=FALSE}
plot(a.model)
```


# Adding a cohort effect on the claim development model

By adding a cohort component to the claim development model, we improve the scaled-deviance residuals. The scaled-deviance residuals can be plotted using the `plot` function on the output of the `clmplus` method.

```{r amodel residuals}
#make it triangular
plot(a.model.fit)
```

The red and blue areas suggest that there are some trends that the age-model wasn't able to catch.


```{r message=FALSE, warning=FALSE}
ac.model.fit <- clmplus(pp_data, 
                    hazard.model="ac")

ac.model <- predict(ac.model.fit,
                    gk.fc.model='a')
plot(ac.model.fit)
```
The fitted effect are displayed below. The cohort component is extrapolated for the last available accident period as discussed in our paper.


```{r message=FALSE, warning=FALSE}

plot(ac.model)

```

## Modelling a period effect on the claim development

It is also possible to add a period component and choose an age-period model or an age-period-cohort model.

```{r apapc models, message=FALSE, warning=FALSE}
ap.model.fit = clmplus(pp_data,
                   hazard.model = "ap")

ap.model<-predict(ap.model.fit, 
                   ckj.fc.model='a',
                   ckj.order = c(0,1,0))

apc.model.fit = clmplus(pp_data,hazard.model = "apc")

apc.model<-predict(apc.model.fit, 
                   gk.fc.model='a', 
                   ckj.fc.model='a',
                   gk.order = c(1,1,0),
                   ckj.order = c(0,1,0))
```

There is no clear difference between the residuals plot obtained using an age-period model compared to the residuals plot obtained using the age-cohort model. Conversely, the plot seems to improve using an age-period-cohort model. 

```{r residuals apmodel}
plot(ap.model.fit)
```


```{r residuals apcmodel}
plot(apc.model.fit)
```

Below, the effects of the age-period-cohort model.

```{r apc effects, message=FALSE, warning=FALSE}
plot(apc.model)
```

# References






